---
title: "An Analysis of ORTG in Lineups"
author: "Jeremy Patak"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(include = FALSE)
```

## Introduction

*Basketball on Paper* by Dean Oliver is the most classic book on basketball analytics available, and odds are that if you're reading this, you've probably read it. I was recently looking back through parts of it and really enjoyed **Chapter 19: The Problem with Scorers**.

Oliver starts the chapter by talking about a young star named Allen Iverson (Yeah, the book is pretty old now). He talks about Iverson's high usage, and that if he focused on a better shot selection, he could improve his efficiency and his individual offensive rating. However, this was a bait-and-switch by Oliver to shift our eyes from what is actually important. He goes on to prove that the ORTG of the *team* is actually better when Iverson carries a very high usage, because it allows his teammates to essentially max out their efficient. He finishes out the chapter by discussing how you can use these principles to "optimize offense".

Over 20 years later, I wanted to take a stab at these ideas and analyze some moves that happened this NBA offseason through the lens of *Basketball on Paper, Chapter 19*.

## Offensive Skill Curves
```{r data}
library(pacman)
p_load(tidyverse)

player_data = read.csv("player_game_data.csv")
```

The offensive skill curve is the building block of this chapter by Oliver. It essentially shows how a player can produce higher offensive ratings when they don't have to carry as much of the load on offense. Or, vice versa, it shows that the higher usage a player accounts for, the less efficient they can be with it.

To start my analysis, I want to get into how these offensive skill curves are constructed.


